\documentclass[11pt,a4paper]{article}

% Basic packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{hyperref}

% Page geometry
\geometry{margin=1in}

% Title spacing
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Header and footer
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\scriptsize Yufei Sun - CV}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Hyperref setup
\hypersetup{
unicode=true,
pdftitle={Yufei Sun: CV (Curriculum Vitae)},
pdfauthor={Yufei Sun},
colorlinks=true,
linkcolor=blue,
citecolor=blue,
urlcolor=blue,
breaklinks=true
}
\urlstyle{same}

\begin{document}
\centerline{\huge \bf Yufei Sun}
\vspace{2mm}
\hrule
\vspace{2mm}
\centerline{Department of Political Science, Tsinghua University, Beijing, China}
\centerline{\emph{Phone:} +86 186 3875 0921 \emph{Email:} \href{mailto:syfyufei@gmail.com}{\nolinkurl{syfyufei@gmail.com}} \hspace{1mm} \emph{Website:} \href{https://adriansun.drhuyue.site/}{\tt adriansun.drhuyue.site}}
\vspace{2mm}
\hrule

\section*{EDUCATION}
2020.09 - Present Ph.D. candidate\hfill Department of Political Science, Tsinghua University
\hfill GPA: 1/89 National Scholarship for Graduate Students
2016.09 - 2020.06 Bachelor of Laws\hfill School of Political Science, Shandong University
\hfill GPA: 1/23 National Scholarship for Undergraduate Students

\section*{Professional Positions}
2021.10 - Present Campus Experts, GitHub\hfill United States
2020.09 - Present R Workshop Lecturer, Tsinghua University\hfill China

\section*{PUBLICATIONS}
\subsection*{Peer-Reviewed Articles}
\begin{spacing}{1}
\textbf{Sun Yufei}, Yang Xuedong. 2023. "The capacity space of local governance and the transmission variation of epidemic prevention and control pressure —Empirical research based on local epidemic prevention and control policies during the Spring Festival in 2021", \textit{Journal of Guangzhou University (Social Science Edition)} 2023(02 vol 22): 71-81.\hfill CSSCI
\end{spacing}

\begin{spacing}{1}
Yue Hu, \textbf{Yufei Sun (Corresponding Author)}, and Donald Lien. 2022. "The Resistance and Resilience of National Image Building: An Empirical Analysis of Confucius Institute Closures in the USA." The Chinese Journal of International Politics 15(2): 209-26.\hfill SSCI Q1 (IF 3.449)
\end{spacing}

\begin{spacing}{1}
Zhen Li, and \textbf{Yufei Sun (Corresponding Author)}. 2021. "Why nudge policies are needed: Understanding the asynchrony of residents'health awareness and behavior." Public Management and Policy Review (01 vo 10): 31-41.\hfill CSSCI
\end{spacing}

\begin{spacing}{1}
Zequn Zhao, \textbf{Yufei Sun}, and Yi Qiu. 2021. "Influencing Factors, Problems and Prospects of Satisfaction in Higher Vocational Major Choice - Individual Students' Perspective." China Vocational and Technical Education (19): 82-86.\hfill AMI
\end{spacing}

\begin{spacing}{1}
Zhen Li, Haoyu Wang, \textbf{Yufei Sun} et al. 2020. "Grassroots governance under the 'emphasis on all areas' subcontracting system—taking the targeted poverty alleviation work of township governments in T district as an example." Public Administration Review (03 vo 13): 102-117+196-197.\hfill CSSCI
\end{spacing}

\begin{spacing}{1}
\textbf{Sun Yufei}. 2020. "The crisis of great power image: changes and influencing factors of China's overseas grassroots image during the COVID-19 outbreak." Bachelor of Laws Thesis, Shandong University.\hfill Outstanding Graduates
\end{spacing}

\subsection*{Softwares}
\begin{spacing}{1}
Yue Hu, \textbf{Yufei Sun}, and Wenquan Wu. 2021. "Regioncode: Convertor of Prefectural-Level Administrative Region Names-Codes." \url{https://CRAN.R-project.org/package=regioncode}.
\end{spacing}

\begin{spacing}{1}
Yue Hu, and \textbf{Yufei Sun}. 2020. "Drhur: Interactive Platform for Liberal Arts Students to Learn R." \url{https://cran.r-project.org/web/packages/drhur/index.html}.
\end{spacing}

\begin{spacing}{1}
\textbf{Yufei Sun}. 2020. "Getgdelt: Get and Use Gdelt Data More Reliably without Hardware Limitation." \url{https://github.com/syfyufei/getgdelt}.
\end{spacing}

\subsection*{Book Chapters}
\begin{spacing}{1}
\textbf{Yufei Sun}. 2023. "Natural Language Processing." In Introduction to Computational Social Sciences, Beijing, China: Tsinghua University Press.
\end{spacing}

\section*{CONFERENCES}
\begin{spacing}{1}
\textbf{Yufei Sun}, Ziyi Chen, and Yue Hu. 2023. Public Management Research Conference 2023. "Non-altruistic Collectivists: Public Service Motivation under Peer Pressure." In Utrecht, Netherlands.(Also oral presentation at APSA 2023.)
\end{spacing}

\begin{spacing}{1}
\textbf{Yufei Sun}. 2023. IAMCR 2023 (OCP). "Parroting for What: The Differential Diffusion of Official Political Discourse - Evidence from Mainland China and Macao SAR." In Lyon, France.(Also gave an oral presentation at the Annual Macau Research Conference 2023)
\end{spacing}

\begin{spacing}{1}
Yue Hu, \textbf{Yufei Sun}, Ziyi Chen. 2023. Modernization of local governance: Seminar on practice and theoretical construction in China. "Seeking for oneself or others: Research on the motivation mechanism of public service motivation" In Xinmi, China
\end{spacing}

\begin{spacing}{1}
Hu, Yue, \textbf{Yufei Sun}, and Donald Lien. 2022. SPSA. "Resisting National Image Building: The Motivators and Consequences of Confucius Institute Closures in the U.S." In San Antonio, US (and also at the 7th "Frontier Theory and Methods of Political Science" Beijing, China)
\end{spacing}

\begin{spacing}{1}
\textbf{Yufei Sun}, Yang Xuedong. 2021. The 5th Academic Symposium on Local Government and Regional Governance. "Insufficient Ability and Pressure to Make Up: Governance Capacity and Pressure-type System - An Empirical Study Based on Local Epidemic Prevention and Control Policies during the Spring Festival in 2021". In Tianjin, China. (Also at the Tsinghua University Doctoral Forum 2023 and got the award of "Excellent oral presentation")
\end{spacing}

\begin{spacing}{1}
Yue Hu, \textbf{Yufei Sun}, Su Y-S. 2021. The 4th China Political Communication Research Academic Forum. "Diversity Loyalty: Psychological Paths of Mass Response to Political" In China, Beijing.
\end{spacing}

\begin{spacing}{1}
\textbf{Yufei Sun}, Ni Tang. 2021. The 9th "Political Culture, Psychology and Behavior Research" Workshop. "Educational Propaganda and Propaganda Education: An Integrated Framework for Political Propaganda Effects - An Experiment Based on Ideological and Political Course Teaching Study" Nanjing, China.
\end{spacing}

\section*{AWARDS \& HONORS}
\begin{spacing}{1}
2023 Second Class Scholarship\hfill Tsinghua University
\end{spacing}

\begin{spacing}{1}
2022 First Class Scholarship\hfill Tsinghua University
\end{spacing}

\begin{spacing}{1}
2021 National Scholarship (Graduate Students)\hfill Ministry of Education of China
\end{spacing}

\begin{spacing}{1}
2021 Tsinghua University "International Student Work Award"\hfill Tsinghua University
\end{spacing}

\begin{spacing}{1}
2020 Outstanding Graduates of Shandong Province\hfill Government of Shandong Province
\end{spacing}

\begin{spacing}{1}
2019, 2018, 2017 First Class Scholarship\hfill Shandong University
\end{spacing}

\begin{spacing}{1}
2018, 2017 National Scholarship (Undergraduate)\hfill Ministry of Education of China
\end{spacing}

\section*{SKILLS}
\subsection*{Analytical}
\begin{spacing}{1}
R, Python, STATA, SPSS, CiteSpace
\end{spacing}

\subsection*{Applied}
\begin{spacing}{1}
\LaTeX, Markdown, Git, FinalcutPro
\end{spacing}

\subsection*{Language}
\begin{spacing}{1}
Mandarin, English
\end{spacing}

\end{document}
